### 2021-03-25 README.Rmd
ADD ZENODO DOI BADGE

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/main?urlpath=rstudio)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/main?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4638221.svg)](https://doi.org/10.5281/zenodo.4638221)
<!-- badges: end -->
